Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-05 paper/main.tex
restructure quotes of anterior vs. posterior PPA v2

% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
\citep{baldassano2013differential} in general: anterior and posterior PPA
exhibit distinct connectivity patterns; object sensitivity in the PPA also has
an anterior-posterior gradient; connectivity gradient was also paired with a
functional gradient of sensitivity to scene and abstract object stimuli.

% gradient
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, and the parahippocampal region (at least in
macaques) is densely self- connected (Suzuki, 2009), implying that these
subregions cooperate to build a complete representation of a scene. Their
distinct connectivity properties, however, suggests that each may be involved in
specific aspects of visual and cognitive processing involved in the overarching
goal of scene understanding.

% from Baldassano discussion
\citep{baldassano2013differential} regarding posterior PPA: posterior regions
are more functionally connected to visual processing regions; posterior PPA more
strongly connected to occipital visual regions; stronger responses to abstract
objects in posterior PPA; posterior PPA is concerned primarily with perception
of low-level visual fea- tures and object shape.

\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
shows a stronger response to abstract objects than anterior PPA, and is more
strongly connected to all of occipital visual cortex, including LOC and TOS.
These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape. Previous work has hinted that posterior PPA is more responsive
to both simple visual textures and objects; Arcaro et al. (2009) found that a
posterior portion of PPA responded about four times as strongly to a flickering
checker-board stimulus compared to an anterior portion, and that the response to
objects was greater than the response to scrambled images only in the posterior
portion => posterior PPA may be more visually responsive than anterior PPA. Our
description of posterior PPA is in fact similar to the original proposal of
Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
which was “specialized for the perception of visual stimuli with orienting
value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
Although the LLA is no longer identified as an independent region from PPA in
current studies, it is possible that the posterior portion of PPA corresponds to
the properties of the proposed LLA, offring an explanation for why this region
was localized more posteriorly than the full PPA.

\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
more functionally connected to retrosplenial complex (RSC) and parietal
cortices; anterior PPA is more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway); anterior PPA is
involved in memory and global contextual processing; anterior PPA is
specifically connected to RSC, cIPL, medial PFC, and the lateral surface of the
anterior temporal lobe. This portion of PPA is less visually responsive to both
scenes and objects, with notably low sensitivity to abstract object stimuli.

\citep{baldassano2013differential} regarding DMN: the set of regions connected
more strongly to anterior PPA is strikingly similar to the Default Mode Network
(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
known to include the parahippocampal region. The only portions of the DMN that
do not show differential connectivity to anterior PPA in our data are the
rostral portion of the posterior cingulate cortex (PCC) and the superior frontal
cortex.  DMN has been implicated in a large number of internally-focused tasks,
one of its key roles involves autobiographical memory (Buckner et al., 2008).
Models of recognition memory have previously identified parahippocampal cor- tex
as primarily encoding spatial context information (Eichenbaum et al., 2007).
Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
may be involved in recall based on spatial context. Our results are consistent
with anterior PPA playing a more central role in memory than posterior PPA,
given anterior PPA's connectivity with the DMN. The fact that anterior PPA had a
lower sensitivity to our abstract object stimuli does not necessarily im ply
that this region does not use object information. Previous work has shown that
PPA responds to objects that have spatial associations (Aminoff et al., 2007),
are space-defining (Mullally and Maguire, 2011), and are navigationally-
relevant (Janzen and Van Turennout, 2004). These types of responses require
spatial memory and cannot be based purely on visual features like object shape.
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation. Further experiments will be required to determine what
type of object-related information is used in this region.

>>>>

% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
\citep{baldassano2013differential} in general: anterior and posterior PPA
exhibit distinct connectivity patterns; object sensitivity in the PPA also has
an anterior-posterior gradient of sensitivity to scene and abstract object
stimuli.

% gradient
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, and the parahippocampal region (at least in
macaques) is densely selfconnected (Suzuki, 2009), implying that these
subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, suggests that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

% from Baldassano discussion
\citep{baldassano2013differential} regarding posterior PPA: posterior regions
are more functionally connected to visual processing / occipital visual regions;
stronger responses to abstract objects in posterior PPA; posterior PPA is
concerned primarily with perception of low-level visual features and object
shape.

\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
shows a stronger response to abstract objects than anterior PPA, and is more
strongly connected to all of occipital visual cortex, including LOC and TOS.
%
These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape.
%
Previous work has hinted that posterior PPA is more responsive to both simple
visual textures and objects; Arcaro et al. (2009) found that a posterior portion
of PPA responded about four times as strongly to a flickering checker-board
stimulus compared to an anterior portion, and that the response to objects was
greater than the response to scrambled images only in the posterior portion =>
posterior PPA may be more visually responsive than anterior PPA.
%
Our description of posterior PPA is in fact similar to the original proposal of
Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
which was “specialized for the perception of visual stimuli with orienting
value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
%
Although the LLA is no longer identified as an independent region from PPA in
current studies, it is possible that the posterior portion of PPA corresponds to
the properties of the proposed LLA, offring an explanation for why this region
was localized more posteriorly than the full PPA.

\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
more functionally connected to retrosplenial complex (RSC) and parietal
cortices; anterior PPA is more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway)
%
anterior PPA is involved in memory and global contextual processing; anterior
PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral surface
of the anterior temporal lobe.
%
This portion of PPA is less visually responsive
to both scenes and objects, with notably low sensitivity to abstract object
stimuli.

\citep{baldassano2013differential} regarding DMN: the set of regions connected
more strongly to anterior PPA is strikingly similar to the Default Mode Network
(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
known to include the parahippocampal region.
%
The only portions of the DMN that do not show differential connectivity to
anterior PPA in our data are the rostral portion of the posterior cingulate
cortex (PCC) and the superior frontal cortex.  DMN has been implicated in a
large number of internally-focused tasks, one of its key roles involves
autobiographical memory (Buckner et al., 2008).  Models of recognition memory
have previously identified parahippocampal cortex as primarily encoding spatial
context information (Eichenbaum et al., 2007).
%
Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
may be involved in recall based on spatial context.
%
Our results are consistent with anterior PPA playing a more central role in
memory than posterior PPA, given anterior PPA's connectivity with the DMN. The
fact that anterior PPA had a lower sensitivity to our abstract object stimuli
does not necessarily im ply that this region does not use object information.
%
Previous work has shown that PPA responds to objects that have spatial
associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape.#
%
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation.
%
Further experiments will be required to determine what type of object-related
information is used in this region.
